---
output:
  pdf_document: default
---

```{r, results = 'hide', message=F, warning=F}
library(quantmod)
library(quantstrat)
setwd("~/git/homework-uw/CFRM522/hw2")
```

# Part I

```{r, results = 'hide', message=F, warning=F}
NG <- read.table("NaturalGas.csv", TRUE, ",")
NG <- xts(
  NG[c("Open", "High", "Low", "Close")], as.Date(NG$Date, format="%d-%b-%y")
)
strAcco <- strPort <- strStra <- "ClenowOneOpt"
rm.strat(strStra)
strategy(strStra, store = TRUE)
add.indicator(strStra, "SMA", list(x = Cl(NG), n = 10), label = "SMA_fast")
add.indicator(strStra, "SMA", list(x = Cl(NG), n = 100), label = "SMA_slow")
add.signal(
  strStra, "sigCrossover",
  list(columns = c("SMA_fast", "SMA_slow"), relationship = "gte"),
  label = "long"
)
add.signal(
  strStra, "sigCrossover",
  list(columns = c("SMA_fast", "SMA_slow"), relationship = "lt"),
  label = "short"
)
add.rule(
  strStra, "ruleSignal",
  list(
    sigcol = "long", sigval = TRUE, orderside = "long", ordertype = "market",
    orderqty = 15, TxnFees = 0, replace = FALSE
  ),
  type = "enter", label = "EnterLong"
)
add.rule(
  strStra, "ruleSignal",
  list(
    sigcol = "short", sigval = TRUE, orderside = "short", ordertype = "market",
    orderqty = -15, TxnFees = 0, replace = FALSE
  ),
  type = "enter", label = "EnterShort"
)
add.rule(
  strStra, "ruleSignal",
  list(
    sigcol = "short", sigval = TRUE, orderside = "long", ordertype = "market",
    orderqty = "all", TxnFees = 0, replace = TRUE
  ),
  type = "exit", label = "ExitLong"
)
add.rule(
  strStra, "ruleSignal",
  list(
    sigcol = "long", sigval = TRUE, orderside = "short", ordertype = "market",
    orderqty = "all", TxnFees = 0, replace = TRUE
  ),
  type = "exit", label = "ExitShort"
)

strCurrency <- "USD"
strSymbol <- "NG"
currency(strCurrency)
future(strSymbol, strCurrency, 1e4, 0.01)
initPortf(strPort, strSymbol)
initAcct(strAcco, strPort, initEq = 1e6)
initOrders(strPort)
applyStrategy(strStra, strPort)
updatePortf(strPort)
updateAcct(strAcco)
updateEndEq(strAcco)
```

```{r}
tradeStats(strPort, strSymbol)
chart.Posn(strPort)
```

# Part II, rough tuning

```{r, results = 'hide', message=F, warning=F}
myHeatMap <- function(
  metric, paramOne, paramTwo, metricTitle, paramOneTitle, paramTwoTitle
) {
  z <- tapply(metric, list(paramOne, paramTwo), mean)
  x <- as.numeric(rownames(z))
  y <- as.numeric(colnames(z))
  filled.contour(
    x, y, z, color = heat.colors, xlab = paramOneTitle, ylab = paramTwoTitle
  )
  title(metricTitle)
}
add.distribution(
  strStra, "sma", "indicator", "SMA_fast", list(n = seq(0, 24, 6)),
  label = "fast"
)
add.distribution(
  strStra, "sma", "indicator", "SMA_slow", list(n = seq(50, 250, 25)),
  label = "slow"
)
add.distribution.constraint(strStra, "sma", "fast", "slow", "<", "sma")
res <- apply.paramset(strStra, "sma", strPort, account.st = strAcco)
myHeatMap(
  res$tradeStats$Profit.To.Max.Draw, res$tradeStats$fast, res$tradeStats$slow,
  "Profit.To.Max.Draw", "Fast", "Slow"
)
myHeatMap(
  res$tradeStats$Net.Trading.PL, res$tradeStats$fast, res$tradeStats$slow,
  "Net.Trading.PL", "Fast", "Slow"
)
myHeatMap(
  res$tradeStats$Max.Drawdown, res$tradeStats$fast, res$tradeStats$slow,
  "Max.Drawdown", "Fast", "Slow"
)
```

All of the three plots suggest two peaks around same regions, while the metric `Profit.To.Max.Draw` provides the best distinction. Among the two peaks, the one located around (fast, slow)$=(0, 170)$ is more robuster, i.e.\ the metric does not decay significantly while (fast, slow) varying around its proximity.

In the next section, we will generate a heat map of `Profit.To.Max.Draw` around the selected region at a finer granularity.

# Part II, precise tuning

```{r, results = 'hide', message=F, warning=F}
add.distribution(
  strStra, "sma", "indicator", "SMA_fast", list(n = seq(0, 9)), label = "fast"
)
add.distribution(
  strStra, "sma", "indicator", "SMA_slow", list(n = seq(155, 190)),
  label = "slow"
)
res <- apply.paramset(strStra, "sma", strPort, account.st = strAcco)
myHeatMap(
  res$tradeStats$Profit.To.Max.Draw, res$tradeStats$fast, res$tradeStats$slow,
  "Profit.To.Max.Draw", "Fast", "Slow"
)
```

According to this plot, we choose the most robust point (fast, slow)$=(2, 168)$.

In the next section, we will rerun the backtest with the selected parameters.

# Part II, backtest

```{r, results = 'hide', message=F, warning=F}
add.indicator(strStra, "SMA", list(x = Cl(NG), n = 2), label = "SMA_fast")
add.indicator(strStra, "SMA", list(x = Cl(NG), n = 168), label = "SMA_slow")
strAcco <- strPort <- "bazinga"
initPortf(strPort, strSymbol)
initAcct(strAcco, strPort, initEq = 1e6)
initOrders(strPort)
applyStrategy(strStra, strPort)
updatePortf(strPort)
updateAcct(strAcco)
updateEndEq(strAcco)
```

```{r}
tradeStats(strPort, strSymbol)
chart.Posn(strPort)
```

The strategy is significantly improved since the following metrics are improved.

|          | Net.Trading.PL | Avg.Trade.PL | Ann.Sharpe | Max.Drawdown |
|----------|---------------:|-------------:|-----------:|-------------:|
| (10,100) |        -378000 |     -4265.73 | -0.4466245 |     -2476200 |
|  (2,168) |        1574850 |     11911.63 |  1.6006510 |     -1312350 |
